---
title: "Project Report Draft"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(tidyverse)
library(readxl)
library(plotly)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%", 
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

<style type="text/css">

h1.title {
  text-align: center;
}

</style>

## Motivation


## Questions

1. 

2. 

3. 

## Data 

### **Data Sources**

Our primary data source is the [NYC Work and Family Leave Survey (WFLS)](https://data.cityofnewyork.us/Health/New-York-City-Work-and-Family-Leave-Survey-WFLS-20/grnn-mvqe).

The NYC WFLS is a telephone survey conducted in March 2016, which was administered to 1,000 New York City residents who gave birth in 2014. The goal was to understand the availability and accessibility of paid family leave to working parents. The WLFS also sought to describe the role that paid family leave policies play in achieving health equity for parents and children.

### **Variables of interest***

**Outcomes**

 * `leave_weeks` = weeks of maternity leave (paid or unpaid)
 * `paid_leave_weeks` = weeks of paid maternity leave 
 * `unpaid_leave_weeks` = weeks of unpaid maternity leave
 * others....
 
**Predictors**
 
 * list...

### **Data Cleaning**

Read in dataset and select variables for analysis

```{r}
wfls_df = 
  read_csv("./data/WFLS_2014.csv") %>% 
  select("resp", "mp1", "ph1", "bc2", "pph1":"el3", "el9", "el11":"cp1", "mh1", "mh4", "cc1", "fixd2":"d7", "st2":"es4", "SAMP_WEIGHT", "POP_WEIGHT", "stratum")
```

Create single race variable

(We should think a bit about how to approach race. Right now I made all people who mentioned more than one race a separate category but this may not be best. If we keep this we should remove d4_3 to d4_6)

```{r}
wfls_df =
  wfls_df %>% 
  mutate(d4_1 = as.character(d4_1)) %>% 
  mutate(
    race = recode(d4_1,
         '1' = "White",
         '2' = "Black/African American",
         '3' = "Asian",
         '4' = "Native Hawaiian/ OPI",
         '5' = "American Indian / AN",
         '8' = "Other")) %>% 
```



#### **NYC Health Report and Related Work**