---
title: "Project Report Draft"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(tidyverse)
library(readxl)
library(plotly)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%", 
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

<style type="text/css">

h1.title {
  text-align: center;
}

</style>

## Motivation


## Questions

1. 

2. 

3. 

## Data 

### **Data Sources**

Our primary data source is the [NYC Work and Family Leave Survey (WFLS)](https://data.cityofnewyork.us/Health/New-York-City-Work-and-Family-Leave-Survey-WFLS-20/grnn-mvqe).

The NYC WFLS is a telephone survey conducted in March 2016, which was administered to 1,000 New York City residents who gave birth in 2014. The goal was to understand the availability and accessibility of paid family leave to working parents. The WLFS also sought to describe the role that paid family leave policies play in achieving health equity for parents and children.

### **Variables of interest***

**Outcomes**

 * `leave_weeks` = weeks of maternity leave (paid or unpaid)
 * `paid_leave_weeks` = weeks of paid maternity leave 
 * `unpaid_leave_weeks` = weeks of unpaid maternity leave
 * others....
 
**Predictors**
 
 * `zip_code` = zip code
 * `race` = race of survey respondent
 * `income` = family income as percent of the federal poverty level
 * `food_insecurity` = concern about having enough food to feed family or recieves public assistance in the form of SNAP benefits / food stamps
 * `education` = highest grade or year of school completed

### **Data Cleaning**

Read in dataset, create weeks of family leave variable, and select variables for analysis

NOTE: unpaid_leave_weeks needs to be fixed to make 77 and 99 NAs - also it's not always matching leave_type so we'll need to choose which one to trust

```{r}
wfls_df = 
  read_csv("./data/WFLS_2014.csv") %>% 
  mutate(
    recode_el12_1 = case_when(
      el12_1 == '1' ~ "0"), 
    recode_el12mns = el12mns*4,
    el11 = as.character(el11),
    leave_type = case_when(
      el11 == '1' ~ "Paid",
      el11 == '2' ~ "Unpaid",
      el11 == '3' ~ "Both",
      el11 == '4' ~ "Did not take time off"),
    leave_weeks = coalesce(recode_el12mns, el12wks),
    unpaid_leave_weeks = el13d,
    pct_unpaid = round((unpaid_leave_weeks/leave_weeks)*100),4) %>% 
  select("resp", "mp1", "ph1", "bc2", "pph1":"el3", "el9", "el11", "el13a":"cp1", "mh1", "mh4", "cc1", "fixd2":"d7", "st2":"es4", "SAMP_WEIGHT":"stratum", "leave_type": "pct_unpaid")
```

Create single race variable

```{r}
wfls_df =
  wfls_df %>% 
  mutate(
    d4_1 = as.character(d4_1),
    d3 = as.character(d3)) %>% 
  mutate(
    multiple_races = as.numeric(d4_2 %in% c(1:8)),
    hispanic = as.numeric(d3 %in% c(1))) %>% 
  mutate(
    race = case_when(
      d4_1 == '1' ~ "White",
      d4_1 == '2' ~ "Black/African American",
      d4_1 == '3' ~ "Asian",
      d4_1 == '4' ~ "Native Hawaiian/OPI",
      d4_1 == '5' ~ "American Indian/AN",
      d4_1 == '8' ~ "Other",
      hispanic == 1 ~ "Hispanic",
      multiple_races == 1 ~ "Multiple")) %>% 
  drop_na(race)
```

Exploratory chart of length of maternity leave by race / ethnicity 

```{r}
wfls_df %>% 
  group_by(leave_weeks, race) %>%
  summarize(mean_leave_weeks = mean(leave_weeks)) %>%
  mutate(race = fct_reorder(race, mean_leave_weeks)) %>%
  ggplot(aes(x = race, fill = race)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, hjust =1), legend.position = "none") +
  labs(
    title = "Average weeks of maternity leave by race",
    x = "Race",
    y = "Mean weeks of leave"
  )
```


## NYC Health Report and Related Work