---
title: "Project Report Draft"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(tidyverse)
library(readxl)
library(plotly)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%", 
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

<style type="text/css">

h1.title {
  text-align: center;
}

</style>

## Motivation


## Questions

1. How does length of maternity leave taken by women in New York City vary according to key socioeconomic characteristics?

2. How does length of maternity leave differ by zip code? Do these spacial patterns match the distribution of key socioeconomic characteristics?

3. Is the geographic distribution of average length of maternity leave associated with X, Y, X?

## Data 

### **Data Sources**

Our primary data source is the [NYC Work and Family Leave Survey (WFLS)](https://data.cityofnewyork.us/Health/New-York-City-Work-and-Family-Leave-Survey-WFLS-20/grnn-mvqe).

The NYC WFLS is a telephone survey conducted in March 2016, which was administered to 1,000 New York City residents who gave birth in 2014. The goal was to understand the availability and accessibility of paid family leave to working parents. The WLFS also sought to describe the role that paid family leave policies play in achieving health equity for parents and children.

### **Variables of interest***

**Outcomes**

 * `leave_weeks` = weeks of maternity leave (paid or unpaid)
 * `paid_leave_weeks` = weeks of paid maternity leave 
 * `unpaid_leave_weeks` = weeks of unpaid maternity leave
 * `postpartum_check` = had a postpartum checkup 4-6 weeks after giving birth
 
**Predictors**

 * `zip_code` = zip code
 * `race` = race of survey respondent
 * `income` = family income as percent of the federal poverty level
 * `food_insecurity` = concern about having enough food to feed family or receives public assistance in the form of SNAP benefits / food stamps
 * `education` = highest grade or year of school completed
 * `partner` = co-parenting status (single or co-parent)
 * `fmla` = access to FMLA
 * `employment_type` = type of employment during pregnancy (government, private company, non-profit, self-employed)

### **Data Cleaning**

Read in data, create weeks of family leave variables, and select variables for analysis

(for some reason leave type doesn't always match up with number of unpaid leave weeks -- we'll have to decide which to trust)

```{r}
wfls_df = 
  read_csv("./data/WFLS_2014.csv") %>% 
  mutate(
    recode_el12mns = el12mns*4,
    el11 = as.character(el11),
    leave_type = case_when(
      el11 == '1' ~ "Paid",
      el11 == '2' ~ "Unpaid",
      el11 == '3' ~ "Both",
      el11 == '4' ~ "Did not take time off"),
    leave_weeks = coalesce(recode_el12mns, el12wks),
    leave_weeks = na_if(leave_weeks, 77),
    leave_weeks = na_if(leave_weeks, 99),
    unpaid_leave_weeks = el13d,
    unpaid_leave_weeks = na_if(unpaid_leave_weeks, 77),
    unpaid_leave_weeks = na_if(unpaid_leave_weeks, 99),
    pct_unpaid = round((unpaid_leave_weeks/leave_weeks)*100),4) %>% 
  select("resp", "mp1", "ph1", "bc2", "pph1":"el3", "el9", "el11", "el13a":"cp1", "mh1", "mh4", "cc1", "fixd2":"d7", "st2":"es4", "SAMP_WEIGHT":"stratum", "leave_type": "pct_unpaid")
```

Create single race variable

```{r}
wfls_df =
  wfls_df %>% 
  mutate(
    d4_1 = as.character(d4_1),
    d3 = as.character(d3)) %>% 
  mutate(
    multiple_races = as.numeric(d4_2 %in% c(1:8)),
    hispanic = as.numeric(d3 %in% c(1))) %>% 
  mutate(
    race = case_when(
      d4_1 == '1' ~ "White",
      d4_1 == '2' ~ "Black/African American",
      d4_1 == '3' ~ "Asian",
      d4_1 == '4' ~ "Native Hawaiian/OPI",
      d4_1 == '5' ~ "American Indian/AN",
      d4_1 == '8' ~ "Other",
      hispanic == 1 ~ "Hispanic",
      multiple_races == 1 ~ "Multiple")) %>% 
  drop_na(race)
```

Save cleaned data set

```{r}
write.csv(wfls_df, "./data/cleaned_wfls.csv")
```


Exploratory chart of average length of maternity leave by race / ethnicity 

```{r}
wfls_df %>% 
  group_by(leave_weeks, race) %>%
  summarize(mean_leave_weeks = mean(leave_weeks)) %>%
  mutate(race = fct_reorder(race, mean_leave_weeks)) %>%
  ggplot(aes(x = race, fill = race)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, hjust =1), legend.position = "none") +
  labs(
    title = "Average weeks of maternity leave by race",
    x = "Race",
    y = "Mean weeks of leave"
  )
```

## NYC Health Report and Related Work